---
title: "Joseph-J-HWK5-3"
author: "Justin Joseph"
date: "2023-04-22"
output:
  pdf_document:
    toc: no
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
  html_document:
    toc: no
    df_print: paged
header-includes: \usepackage{booktabs}
---
```{r, echo = FALSE, message = FALSE, warning = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata)
library(tidyverse)
library(scales)
library(knitr)
library(rdrobust)
library(modelsummary)
library(AER)
library(fixest)
library(acs)
library("kableExtra")
```

```{r, include=FALSE}
load("Hwk5_workspace_5_3.Rdata")
```

### 1. 

```{r figure1, warning=FALSE, echo=FALSE, fig.cap="Share of insured individuals with direct purchase health insurance between 2012 to 2019."}
Q1
```

\newpage


### 2.
Because of the creation of the ACA marketplace there is a reduction in direct purchase health insurance for two reasons. One because of the ACA's regulations in making health insurance more equitable in terms of non price discriminating based on pre-existing health conditions. Because of this mandate some private health insurances had to increase their premiums to protect against this potential risk. In addition, another reason there may have been a decrease in direct purchase health insurance is the fact that the ACA created a subsidized marketplace for consumers to purchase health insurance directly from private firms at a lower rate. Thus this alternative to direct purchase may be more cost effective for consumers and push them away from directly being from an insurance provider and using the marketplace as a cheaper option. Risk corridor and re insurance were meant to reduce premiums but after a few years after 2014  thye were stopped so may of caused a s deacrease in direct insurance people
\newpage

### 3. 
```{r figure2, warning=FALSE, echo=FALSE, fig.cap="Share of insured individuals with Medicaid between 2012-2019"}
Q3
```  

\newpage

### 4.

```{r figure3, warning =FALSE, echo=FALSE, fig.cap="Share of uninsure individuals for states that expanded and did not expand medicaid in 2014"}
figure_Q4
```

\newpage

### 5.

```{r, echo=FALSE, fig.align='left'}
kable(Q5_table, col.names = c("Group", "2012 (Pre)", "2015 (Post)"), caption = "The average percent of uninsured individuals in 2012 and 2015 for expansion and non-expansion states", booktabs = TRUE) %>% kable_styling(latex_options=c("hold_position"), full_width = TRUE, position="center")
```
\newpage

### 6.
```{r, echo=FALSE, fig.align='left'}
modelsummary(dd.est,
             title = "The effect of Medicaid expansion on the uninsurance rate using a standard DD regression ",
             gof_map=list(list("raw"="nobs","clean"="N", "fmt"=0),
                          list("raw"="r.squared", "clean"="R\\textsuperscript{2}", "fmt"=2))) %>% kable_styling(latex_options=c("hold_position"), full_width = TRUE, position="center")
```

\newpage

### 7. 
```{r, echo=FALSE}
modelsummary(fe.est,
             title = "The effect of Medicaid expansion on the uninsurance rate using Fixed Effects Estimator ",
             gof_map=list(list("raw"="nobs","clean"="N", "fmt"=0),
                          list("raw"="r.squared", "clean"="R\\textsuperscript{2}", "fmt"=2))) %>% kable_styling(latex_options=c("hold_position"), full_width = TRUE, position="center")
```

\newpage

### 8. 

```{r, echo=FALSE}
modelsummary(fe.est2,
             title = "The effect of Medicaid expansion on the uninsurance rate using a standard DD regression using all states",
             gof_map=list(list("raw"="nobs","clean"="N", "fmt"=0),
                          list("raw"="r.squared", "clean"="R\\textsuperscript{2}", "fmt"=2))) %>% kable_styling(latex_options=c("hold_position"), full_width = TRUE, position="center")
```

The reason we get different estimates is because no we are adding states that expanded after 2014. These states are different from states that expanded right away and thus since we have differently groups we will obtain a different estimates. This estimate is greater than our orginal estimate of just looking at states that expanded in 2014 and thus shows there is a more pronounced effect of a decrease in uninsurance rates by expansion when we add a bigger group of states to our sample to create the estimate. 
\newpage

```{r figure9, warning=FALSE, echo=FALSE, fig.align="center", fig.cap="Event Study for 2014 Treatment Group"}
iplot(Q9, 
                  xlab='Time to treatment',
                  main='')

```  
\newpage
### 10. 
```{r figure10, warning=FALSE, echo=FALSE, fig.align="center", fig.cap="Event Study of Medicaid Expansion for each year (including all states"}
iplot(mod.twfe2, xlab='Time to treatment', main='')

```  